% CREATED BY DAVID FRISK, 2015
\thispagestyle{plain}			% Supress header 
\setlength{\parskip}{0pt plus 1.0pt}

\section*{Abstract}
The use of software in automotive engineering keeps on growing higher every year. This has an impact on a data stored in a database such that a structure of data stored becomes complex due to hierarchy and hence difficult to understand. 
The benefit of being able to visualize a complex data structure of a system facilitates a quick learning of how a system work and a general understanding of where to locate a particular piece of data in a database. 
A large focus in the industries is placed more on innovating new features of a car by improving current software built in a car’s system and also developing new software. There is rather a less focus in visualizing the software which have already been implemented in a car’s system.
The purpose of this study is to provide an automatic visualization of a current implementation of software data that is stored in a database. This visualization is meant to cover the needs of different stakeholders interacting with a database to aid the system’s understanding and facilitate decision making in their work.
Our focus of the study has been understanding the field of automotive software engineering, its architecture, understanding how to get needs of different stakeholders and finally be able to provide the stakeholders with a visualization of data that they may need when interacting with a database.

How was the visualization done?
What were the result, the conclusion?
\todo{[to be filled in]}

% KEYWORDS (MAXIMUM 10 WORDS)
%\vfill
%Keywords: a, b, c. \todo{[to be filled in]}

%\newpage				% Create empty back of side
\thispagestyle{empty}
\mbox{}