% CREATED BY DAVID FRISK, 2015
\begin{thebibliography}{69}

\bibitem{Basili}
Basili, V. and Weiss, D. (1984). A Methodology for Collecting Valid Software Engineering Data. \textit{IEEE Transactions on Software Engineering}, SE-10(6), pp.728-738.

\bibitem{Brambilla}
Brambilla, M., Cabot, J. and Wimmer, M. (2012). \textit{Model-driven software engineering in practice}. [San Rafael, Calif.]: Morgan \& Claypool.

\bibitem{Canovas}
Cánovas Izquierdo, J., \& Cabot, J. (2013). Discovering Implicit Schemas in JSON Data. \textit{13Th International Conference, ICWE 2013, Aalborg, Denmark, July 8-12, 2013. Proceedings}.

\bibitem{community_tool_box}
Community Tool Box (2016). \textit{Chapter 7. Encouraging Involvement in Community Work}. Retrieved from \url{http://ctb.ku.edu/en/table-of-contents/participation/encouraging-involvement/identify-stakeholders/main}

\bibitem{Czarnecki}
Czarnecki, K. and Helsen, S. (2006). Feature-based survey of model transformation approaches. \textit{IBM Syst. J.}, 45(3), pp.621-645.

\bibitem{Dajsuren}
Dajsuren, Y. (2013). Automotive Architecture Description and Its Quality. \textit{Proceedings of the 2013 9th Joint Meeting on Foundations of Software Engineering}, pp.727-730. 

\bibitem{Adam}
Darvas, A. \& Konnerth, R. (2016). \textit{System Architecture Recovery based on Software Structure Model.}, pp.109-114.

\bibitem{Eliasson_1}
Eliasson, U., Heldal, R., Pelliccione, P., \& Lantz, J. (2015). \textit{Architecting in the Automotive Domain: Descriptive vs Prescriptive Architecture}. Software Architecture (WICSA), 2015 12th Working IEEE/IFIP Conference on. IEEE.

\bibitem{Eliasson_2}
Eliasson, U., Martini, A., Kaufmann, R., \& Odeh, S. (2015). \textit{Identifying and visualizing Architectural Debt and its efficiency interest in the automotive domain: A case study}. Managing Technical Debt (MTD), 2015 IEEE 7th International Workshop on. IEEE.

\bibitem{Jean}
Favre, J.M. \& Cervantes, H. (2002). \textit{Visualization of Component-based Software}, 6(2), pp.205-219.

\bibitem{Glanz}
Glanz, J. (1999). \texttt{Action Research} (pp. 22-23). Retrieved from \url{http://www.education.vic.gov.au/Documents/school/teachers/profdev/actionresearchjglanz.pdf}

\bibitem{Grönniger}
Grönniger, H., Hartmann, J., Krahn, H., Kriebel, S., Rothhardt, L., \& Rumpe, B. (2008). View-Centric Modeling of Automotive Logical Architectures. \textit{Tagungsband des Dagstuhl-Workshop MBEES: Modellbasierte Entwicklung eingebetteter Systeme IV}.

\bibitem{Lauesen}
Lauesen, S. (2002). \textit{Software requirements: Styles \& Techniques}. Harlow: Addison-Wesley.

\bibitem{Niesel}
Niesel, K. (2014). \textit{Software center day: The All-New XC90} [PowerPoint slides]. Retrieved from \url{http://softwarecenter.gu.se/digitalAssets/1506/1506474_sw-center---sk--ne-volvo.pdf}

\bibitem{OnlineQDA}
OnlineQDA (2016). Online QDA - \textit{How and what to code}. [online] Available at: \url{http://onlineqda.hud.ac.uk/Intro_QDA/how_what_to_code.php} [Accessed 2 April 2016].

\bibitem{Sjoberg}
Sjoberg, D., Dyba, T., \& Jorgensen, M. (2007). The Future of Empirical Methods in Software Engineering Research. \textit{2007 Future Of Software Engineering}, 358-378. http://dx.doi.org/10.1109/FOSE.2007.30

\bibitem{Stachowiak}
Stachowiak, H. (1973). \textit{Allgemeine Modelltheorie}. Wien, New York: Springer-Verlag.

\bibitem{Stuurman}
Stuurman, G. (2010). \textit{Action Semantics applied to Model Driven Engineering} (Master Thesis). University of Twente.

\bibitem{Tichy}
Tichy, M. \textit{Model-Driven Engineering (MDE) Lecture 3: Meta-Modelling}. Lecture, Chalmers University of Technology.

\bibitem{Beeck}
von der Beeck, M. (2006). Development of logical and technical architectures for automotive systems. \textit{Softw Syst Model}, 6(2), pp.205-219.

\bibitem{Wallin}
Wallin, P. (2008). \textit{Key Challenges in Decision Making for Automotive E/E Architectures} (Licentiate Thesis, Mälardalen University, Västerås, Sweden). Retrieved from \url{http://www.diva-portal.org/smash/get/diva2:127004/FULLTEXT02.pdf} 

\end{thebibliography}
